### 2019-02-28 manuscript/discussion.tex
- a variety of small comment deletions, comments and changes (mainly formatting, etc.)

% - what happens if PD only, Hidden states
Using the most complete dataset for polyploidy in a phylogenetic tree in Solanaceae, we were able to replicate the results found by \citet{mayrose_2011}, polyploids have a slower net diversification compare to diploids
Furthermore,  we also found polyploids had a high probability of having negative diversification which implies that polyploids can become a macroevolutionary dead-end, a result that was also found in the two large angiosperm diversification studies  \citet{mayrose_2011} and \citet{mayrose_2015}
However, we expanded this study to accomodate  background heterogeneity in the diversification process
When adding heterogeneity we found that it was more likely that an unobserved trait linked to diploid state was the one leading the net diversification patterns, and that there were some ``second-class" diploids that were not different from polyploids in diversification terms (Figure 2A)
This result lead us to our central question: \textit{what is that other trait linked diploids that makes them different in the diversification process? }.\newline

%     main finding about our traits
In Solanaceae, our immediate intuition was to look into breeding system
Previous studies shown that self-incompatible Solanaceae species have also higher rates of diversification compared to their self-compatible counterparts\ctiep{goldberg_2012}
Self-incompatible species are diploid in our sample and also expected to be diploid due to ..
(citation?)
By considering both polyploidy and breeding system simultaneously for every species in our sample, it was possible to disentangle why some diploids were quantitatively different than polyploids
In the three-state diversification model ID/CD/CP, we found that self-incompatible diploids have faster and positive rates than self-compatible diploids and polyploids, and that the difference between the  rates of net diversification of self-compatible diploids is not as large (Figures 2C) as first found by binary trait diversification models (Figures 2A)
This result is important, since it aligns with the net diversification results of the  D/P+A/B model, where a ``hidden-trait" seem to be dictating the diversification pattern
By adding breeding system, we were able to hint at which that hidden-trait possibly is
Therefore, we consider that finding a heterogenous result in the hidden trait approaches should be be treated as evidence of a second trait that is necessary to consider
Pursuing knowledge of  such trait can result on a clearer picture of the importance of trait linked diversification patterns, but also on a better reconstruction on past events in phylogenies.

% - diversification  (frame as no-delta first)

>>>>

% - diversification  (frame as no-delta first)
% - what happens if PD only, Hidden states
Using the most complete dataset for polyploidy in a phylogenetic tree in Solanaceae, we were able to replicate the results found by \citet{mayrose_2011}, polyploids have a slower net diversification compare to diploids
Furthermore,  we also found polyploids had a high probability of having negative diversification which implies that polyploids can become a macroevolutionary dead-end, a result that was also found in the two large angiosperm diversification studies  \citet{mayrose_2011} and \citet{mayrose_2015}
However, we expanded this study to accomodate  background heterogeneity in the diversification process
When adding heterogeneity we found that it was more likely that an unobserved trait linked to diploid state was the one leading the net diversification patterns, and that there were some ``second-class" diploids that were not different from polyploids in diversification terms (Figure 2A)
This result lead us to our central question: \textit{what is that other trait linked diploids that makes them different in the diversification process? }.\newline

%     main finding about our traits
In Solanaceae, our immediate intuition was to look into breeding system
Previous studies shown that self-incompatible Solanaceae species have also higher rates of diversification compared to their self-compatible counterparts\citep{goldberg_2012}
Self-incompatible species are diploid in our sample and also expected to be diploid due to ..
(citation?)
By considering both polyploidy and breeding system simultaneously for every species in our sample, it was possible to disentangle why some diploids were quantitatively different than polyploids
In the three-state diversification model ID/CD/CP, we found that self-incompatible diploids have faster and positive rates than self-compatible diploids and polyploids, and that the difference between the  rates of net diversification of self-compatible diploids is not as large (Figures 2C) as first found by binary trait diversification models (Figures 2A)
This result is important, since it aligns with the net diversification results of the  D/P+A/B model, where a ``hidden-trait" seem to be dictating the diversification pattern
By adding breeding system, we were able to hint at which that hidden-trait possibly is
Therefore, we consider that finding a heterogenous result in the hidden trait approaches should be be treated as evidence of a second trait that is necessary to consider
Pursuing knowledge of  such trait can result on a clearer picture of the importance of trait linked diversification patterns, but also on a better reconstruction on past events in phylogenies.

### 2019-02-28 manuscript/main.tex
- suggestions in Results - small modification to supp table legend in Results - check author info note!
- a variety of small comment deletions, comments and changes (mainly formatting, etc.)

%B: I included extended affiliations necessary at submission time. Check, please! 
%B->R you may wish to add new affiliation at Manoa, but I left the original state alone.
\noindent
Rosana Zenil-Ferguson\endnote{Department of Ecology, Evolution, and Behavior, University of Minnesota, Saint Paul, MN 55108, U.S.A.}$^{\dagger}$,
%
\noindent
J.~Gordon Burleigh\endnote{Department of Biology, University of Florida, Gainesville, FL 32611, U.S.A.},
%
\noindent
William A.~Freyman\endnote{23andMe, Inc., 899 W Evelyn Ave, Mountain View, CA 94041, U.S.A.},
%
\noindent
Boris Igi\'c\endnote{Department of Biological Sciences, University of Illinois at Chicago, Chicago, IL 60607, U.S.A. },
%
\noindent
Itay Mayrose\endnote{Department of Molecular Biology and Ecology of Plants, Tel Aviv University, Tel Aviv, Israel},
%
and
Emma E.~Goldberg\endnote{Department of Ecology, Evolution, and Behavior, University of Minnesota, Saint Paul, MN 55108, U.S.A.}
%
\vfill

@@

NSF DEB-1655478.
The Minnesota Supercomputing Institute (MSI) at the University of Minnesota provided computing resources for this project.

>>>>

%B: I included extended affiliations necessary at submission time. Check, please! TODO
%B->R you may wish to add new affiliation at Manoa, but I left the original state alone.
\noindent
Rosana Zenil-Ferguson\endnote{Department of Ecology, Evolution, and Behavior, University of Minnesota, Saint Paul, MN 55108, U.S.A.}$^{,\dagger}$,
%
\noindent
J.~Gordon Burleigh\endnote{Department of Biology, University of Florida, Gainesville, FL 32611, U.S.A.},
%
\noindent
William A.~Freyman\endnote{23andMe, Inc., 899 W Evelyn Ave, Mountain View, CA 94041, U.S.A.},
%
\noindent
Boris Igi\'c\endnote{Department of Biological Sciences, University of Illinois at Chicago, Chicago, IL 60607, U.S.A. },
%
\noindent
Itay Mayrose\endnote{Department of Molecular Biology and Ecology of Plants, Tel Aviv University, Tel Aviv, Israel},
%
and
Emma E.~Goldberg\endnote{Department of Ecology, Evolution, and Behavior, University of Minnesota, Saint Paul, MN 55108, U.S.A.}
%
\vfill

@@

NSF DEB-1655478.
The Minnesota Supercomputing Institute (MSI) at the University of Minnesota provided computing resources for this project.
% Perhaps other's funding sources for max BSF/NSF payoff.

### 2019-02-28 manuscript/methods.tex
notes while talking to Rosana
- a variety of small comment deletions, comments and changes (mainly formatting, etc.)

Chromosome number data were obtained for all Solanaceae taxa in the Chromosome Counts Database \citep[CCDB;][]{rice_2015}, and the ca.~14,000 records were cleaned semi-automatically using the CCDBcurator R package \citep{rivero_2019}. %B: perhaps "cleaned" should be explained, unless it's hard to identically repeat as-is.
This large dataset includes the compilation of Solanaceae ploidy states from \citet{robertson_2011}.
Species were coded as either diploid (D) or polyploid (P).
For the majority of species, ploidy was assigned according to information from the original publications and the Kew Royal Botanic Gardens C-value DNA resource \citep{bennett_2005}.
For taxa without ploidy information but with information about chromosome number, we assigned ploidy based on the multiplicity of chromosomes within the genus.
For example, \textit{Solanum betaceum} did not include information about ploidy level but it has 24 chromosomes, so because $x=12$ is the base chromosome number of the \textit{Solanum} genus \citep{olmstead_2007}, we assigned \textit{S.~betaceum} as diploid. 
Species with more than one ploidy level were assigned the smallest and most frequent ploidy level recorded.
% E: There was more here about cross-verifying that no P species were SI.  I removed it because there were conflicts before, but we resolved them.  This is addressed in the next paragraph.
%
Breeding system was scored as self-incompatible (I) or self-compatible (C) based on results curated from the literature and  original experimental crosses \citep[as compiled in][]{igic_2006, goldberg_2010, robertson_2011, goldberg_2012}.
Most species could unambiguously be coded as either I or C \citep{raduski_2012}.
Following previous work, we coded as I any species with functional I systems, even if C or dioecy was also reported.
Dioecious species without functional I were coded as C.

%B: It would be nice to clarify what was added--what is new--and separate the subsections of ploidy and breeding system data.
%
% E: I am trying to stick with I/C when talking about the state values, but using SI/SC when talking about the meaning of the trait (because this what people use normally).

To those existing data sets, we added some additional records for chromosome number and breeding system.
The Supplementary Information contains citations for the numerous sources for the added data. % todo: add number of refs when we have it
Resolution of taxonomic synonymy followed the conventions provided in Solanaceae Source \citep{solsource}. 
Hybrids and cultivars were excluded because ploidy and breeding system can be affected by artificial selection during domestication.
Following the reasoning outlined in \citet{robertson_2011}, we examined closely the few species for which the merged ploidy and breeding system data indicated the presence of self-incompatible polyploids.
Although SI populations frequently contain some SC individuals, and diploid populations frequently contain some polyploid individuals, in no case did we find a convincing case of a naturally occurring SI and polyploid population.
%B: Thus qualified, as above, I think this should be inserted.
The single instance of an SI and polyploid individual appears to be an allopentaploid hybrid of {\em Solanum oplocense} Hawkes x {\em Solanum gourlayii} Hawkes, reported by \citealt{camadro_1981}.
Under exceedingly rare circumstances, it is possible for polyploids containing multiple copies of S-loci to remain SI, so long as they express a single allele at the S-locus (discussed in \citealt{robertson_2011}).
Because of the resulting absence of SI and polyploid populations, as well as the linked functional explanation for disabling of gametophytic self-incompatibility systems with non-self recognition, following whole genome duplication \citep[reviewed in][]{ramsey_1998,stone_2002}, we consider only three observed character states: self-incompatible diploids (ID), self-compatible diploids (CD), and polyploids which are always self-compatible (CP).
%B: I added the non-self recognition bit, because in Prunus, heteroallelic pollen may not cause SC.
% E: Should we include more details about how many polymorphic species and how the particularly tricky ones were dealt with? %B: No and yes, maybe. Interested parties can go to data for part 1?

@@

@@

%B: we moved back from "SI" to "self-incompatibility" below. Maybe a no-no.
For all breeding system models, we allow transitions from $I$ to $C$ (at rate $q_{IC}$) but not the reverse. %B: was "these and the subsequent models including breeding systems"
Within Solanaceae, self-incompatibility is homologous in all species in which S-alleles were cloned, and controlled crosses performed.  
All species sampled to date, possess a non-self recognition, RNase-based, gametophytic self-incompatibility \citep[shared even shared even with other euasterid families;][]{ramanauskas_2017}. %B: this now makes a narrower claim than igic_2001/steinbachs_2002, which includes Rosaceae and a bag of avoidable troubles. 
Furthermore, species that are distantly related within this family carry closely-related alleles, with deep trans-specific polymorphism, at the S-locus, which controls the SI response \citep{ioerger_1990, igic_2006}. %B: may need to introduce "S-locus" earlier.
This represents very strong evidence that the SI mechanism, and our $I$ state is ancestral to the Solanaceae, and did not arise independently within the family ($q_{CI}=0$). %B: I think I have this right <- someone please double-check.
% This is an important assumption because ancestral state reconstruction in the models might differ when polyploidy and breeding system are analyzed as independent in the Solanaceae tree.
% This irreversibility assumption prevents self-compatible state from evolving into self-incompatible state and as a result, the ancestral state of all taxa in this model has probability one of being self-incompatible.

%B: What happens if SC->SI is not fixed? Asking for a friend.  E: Surprisingly, Rosana reports, results are not turned on their head.

@@

If ploidy and breeding system each influence lineage diversification individually, it is logical to examine their possible joint effects. %B: unsure about edit, which was: "If both ploidy and breeding system have the potential to influence lineage diversification, we should logically consider their effects jointly."
We thus fit a multi-state model that includes both traits \citep[MuSSE,][]{fitzjohn_2012}.
The three states in this model are self-incompatible diploids (ID), self-compatible diploids (CD), and polyploids, which are always self-compatible (CP).
As explained above, we did not include a state for self-incompatible polyploids because they are not observed in the data, and   that trait combination state is mechanistically predicted not to occur.
We call this the \textit{ID/CD/CP ploidy and breeding system} model.
The model has 10 parameters, six for diversification in each state ($\lambda_{ID},\ \lambda_{CD},\ \lambda_{CP}$ for speciation, $\mu_{ID},\ \mu_{CD},\ \mu_{CP}$ for extinction) and four for transitions between states ($\rho_I,\ \rho_C$ for polyploidization transitions from $ID$ and $CD$ to $CP$, respectively; $\delta$ for diploidization from $CP$ to $CD$; $q_{IC}$ for loss of self-incompatibility without polyploidization, from $ID$ to $CD$).
The total rate of loss of self-incompatibility, \ie transitions out of $ID$, is $q_{IC} + \rho_I$.
Diploidization from $CP$ to $ID$ is not allowed because it would represent a simultaneous regain of SI.

The ID/CD/CP model could potentially capture similar dynamics as earlier models, if the effects of the hidden state in D/P+A/B were effectively caused by breeding system (or its correlates), and the hidden state in I/C+A/B was effectively caused by ploidy. % B: I know that causation is not strict here, but it clarifies the intended biological explanation.
There is also the potential, however, for a hidden factor to be influencing diversification beyond both of our focal traits, and this could again mislead inferences.
We therefore added a hidden trait layer on top of our three-state model \citep[analogous to][]{caetano_2018, herrera_2018, huang_2018}.
We refer to this as the \textit{ID/CD/CP+A/B} model.
A fully parameterized version of this model would have 26 rate parameters \citep{herrera_2018}. 
Because our goal was to look for diversification rate differences associated with ploidy and breeding system rather than the specific effects of the hidden states, we fitted a simplified version with 16 parameters.
The reduction in parameter space is achieved by fixing the rates for transitions among hidden states to be equal with rate $\alpha$, and fixing the transition rates between observed states to be independent of the hidden state (rates $\rho_I,\ \rho_C,\ \delta,\ q_{IC}$ as defined for the ID/CD/CP model).
There are additionally twelve diversification rate parameters ($\lambda_{ID_A},\ \lambda_{ID_B},\ \lambda_{CD_A},\ \lambda_{CD_B},\ \lambda_{CP_A},\ \lambda_{CP_B},\ \mu_{ID_A},\ \mu_{ID_B},\ \mu_{CD_A},\ \mu_{CD_B},\ \mu_{CP_A},\ \mu_{CP_B}$).
%B: I can't tell, but it seems to me that this 26->16 parameter reduction makes it possible to underestimate the effect of these hidden states. Perhaps this complication is covered in the Discussion section.

@@

%B: this section needs a motivation. Right now, that appears to be hung on an argument from a citation (mayrose_2010), which is not clarified. I think you guys may have the paleo-WGD literature in mind here. If so, perhaps simply stating something ought to be written about the expectations for capturing some underlying process we think is ongoing.
For all four models that consider ploidy changes, we allowed diploidization.
Previous modeling approaches \citep{mayrose_2011} have argued against inferring diploidization rates when using ploidy data that comes from classifications based on chromosome number multiplicity or chromosome number change models like chromEvol \citep{mayrose_2010}.
These types of classifications do not allow for a ploidy reversion.
Where indicated, the classification of ploidy for the data used in our models was based on chromosome multiplicity at the genus level.
% ref data/sources table?
However, the majority of the ploidy classifications were adopted from original studies with alternative sources of information (\eg geographic distribution, genus ploidy distribution) where ploidy was defined by authors that found evidence for it.
Since it is not clear whether diploidization can be detected under alternative ploidy classifications or even classifications based on chromosome number multiplicity at the genus level, we also fit the models without diploidization in order to test  whether the conclusions about diversification are sensitive to including diploidization.
As discussed by \citet{servedio_2014}, the presence or absence of a hypothesis can have an exploratory goal.
In our case the diploidization parameter (or its absence, $\delta=0$) in our models is an opportunity to explore an assumption that might be important but that is not the single definitive process to understand the interactions among polyploidy, breeding system, and diversification.

% \subsection{Pathways to polyploidy} % E todo
% robertson2011 method, and then with diversification

@@

@@

Using the marginal likelihood values, we calculated thirteen different Bayes factors.
Six compared the models of ploidy against one other (D/P and D/P+A/B, each with or without diploidization), one compared the breeding system models (I/C and I/C+A/B), and six compared the models with both traits (ID/CD/CP and ID/CD/CP+A/B, each with or without diploidization) (\cref{table:bayesfactors}).
%
Other comparisons between these models are not valid because the input data are different under the different state space codings (\cref{figure:stateclassifications}).
In mathematical terms, the D/P, I/C, and ID/CD/CP state spaces are not `lumpable' with respect to one another \citep{tarasov_2019}.
%R: Emma this is where the figure can be important to show that we have to make different input
% E: I think this short explanation is clear enough, especially with the figure.  I'm not sure whether the hierarchical concept is exactly applicable here.
%B: my TeX GUI (and my brain) underlined "lumpable", especially in the context of "with respect to one another." I think I get the gist, but I am not sure that I agree others will easily. I find it useful to imagine Spencer reading this, for example.
% E: "Lumpable" is the math word for a particular relation among state codings, used in that Tarasov paper.  I don't think we want to get into defining it precisely.  Instead, we want Fig 1 to make it intuitively clear, to Spencer and everyone else.  I added to the caption and the text above.  Okay, or more work needed?
Each model comparison is reported with a Bayes factor on the natural log scale: the comparison between models $M_0$ and $M_1$ is $BF(M_0,\ M_1) = \ln[ P(\mathbf{X} | M_0) - P(\mathbf{X} | M_1]$.
There is `positive' support for $M_0$ when this value is more than 2, `strong' support when it is more than 6, and `very strong' support when it is more than 10 \citep{kass1995}.

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{states.pdf}
\caption{
Character states used for each of the models.
Each species retained on the tree belonged to one of five possible categories, depending on whether ploidy and/or breeding system were known.
The number of species in each is shown under the corresponding circles in the top row. % FIXME: Rosana, what are the numbers for CP and ?P ?
These categories were then grouped in a manner appropriate to the states of each model.
For example, there are 34 species that are self-compatible and of unknown ploidy; these are coded as either $D$ or $P$ in the D/P models (uncertain, or consistent with either state), as $C$ in the I/C models, and as either $CD$ or $CP$ in the ID/CD/CP models.
In all cases, species were coded as either $A$ or $B$ in the hidden state models.
The models depicted in the different rows use state spaces that are not comparable with one another.
For example, we cannot test whether the D/P model fits better than the I/C model because they use states that are not the same and are not `lumpable' \citep{tarasov_2019}.
}
\label{figure:stateclassifications}
\end{figure}

>>>>

Chromosome number data were obtained for all Solanaceae taxa in the Chromosome Counts Database \citep[CCDB;][]{rice_2015}, and the ca.~14,000 records were cleaned semi-automatically using the CCDBcurator R package \citep{rivero_2019}. %B: perhaps "cleaned" should be explained, unless it's hard to identically repeat as-is.
This large dataset includes the compilation of Solanaceae ploidy states from \citet{robertson_2011}.
Species were coded as either diploid (D) or polyploid (P).
For the majority of species, ploidy was assigned according to information from the original publications and the Kew Royal Botanic Gardens C-value DNA resource \citep{bennett_2005}.
For taxa without ploidy information but with information about chromosome number, we assigned ploidy based on the multiplicity of chromosomes within the genus.
For example, \textit{Solanum betaceum} did not include information about ploidy level but it has 24 chromosomes, so because $x=12$ is the base chromosome number of the \textit{Solanum} genus \citep{olmstead_2007}, we assigned \textit{S.~betaceum} as diploid. 
Species with more than one ploidy level were assigned the smallest and most frequent ploidy level recorded.
% E: There was more here about cross-verifying that no P species were SI.  I removed it because there were conflicts before, but we resolved them.  This is addressed in the next paragraph.
%
Breeding system was scored as self-incompatible (I) or self-compatible (C) based on results curated from the literature and  original experimental crosses \citep[as compiled in][]{igic_2006, goldberg_2010, robertson_2011, goldberg_2012}.
Most species could unambiguously be coded as either I or C \citep{raduski_2012}. %B: most? Any exceptions?
Following previous work, we coded as I any species with functional I systems, even if C or dioecy was also reported.
Dioecious species without functional I were coded as C.

% E: I am trying to stick with I/C when talking about the state values, but using SI/SC when talking about the meaning of the trait (because this what people use normally).

To those existing data sets, we added some additional records for chromosome number and breeding system.
The Supplementary Information contains citations for the numerous sources for the added data. % todo: add number of refs when we have it
Resolution of taxonomic synonymy followed the conventions provided in Solanaceae Source \citep{solsource}. 
Hybrids and cultivars were excluded because ploidy and breeding system can be affected by artificial selection during domestication.
Following the reasoning outlined in \citet{robertson_2011}, we examined closely the few species for which the merged ploidy and breeding system data indicated the presence of self-incompatible polyploids.
Although SI populations frequently contain some SC individuals, and diploid populations frequently contain some polyploid individuals, in no case did we find a convincing case of a naturally occurring SI and polyploid population.
%B: Thus qualified, as above, I think this should be inserted.
The single instance of an SI and polyploid individual appears to be an allopentaploid hybrid of {\em Solanum oplocense} Hawkes x {\em Solanum gourlayii} Hawkes, reported by \citealt{camadro_1981}.
Under exceedingly rare circumstances, it is possible for polyploids containing multiple copies of S-loci to remain SI, so long as they express a single allele at the S-locus (discussed in \citealt{robertson_2011}).
Because of the resulting absence of SI and polyploid populations, as well as the linked functional explanation for disabling of gametophytic self-incompatibility systems with non-self recognition, following whole genome duplication \citep[reviewed in][]{ramsey_1998,stone_2002}, we consider only three observed character states: self-incompatible diploids (ID), self-compatible diploids (CD), and polyploids which are always self-compatible (CP).
%B: I added the non-self recognition bit, because in Prunus, heteroallelic pollen may not cause SC.
% E: Should we include more details about how many polymorphic species and how the particularly tricky ones were dealt with? %B: No and yes, maybe.

@@

% NOTE: Should subtly rephrase so that the default models lack diploidization.

@@

%B: we moved back from "SI" to "self-incompatibility" below. Maybe a no-no.
For all breeding system models, we allow transitions from $I$ to $C$ (at rate $q_{IC}$) but not the reverse.
Within Solanaceae, self-incompatibility is homologous in all species in which S-alleles were cloned, and controlled crosses performed.  
All species sampled to date, possess a non-self recognition, RNase-based, gametophytic self-incompatibility \citep[shared even with other euasterid families;][]{ramanauskas_2017}.
Furthermore, species that are distantly related within this family carry closely-related alleles, with deep trans-specific polymorphism, at the S-locus, which controls the SI response \citep{ioerger_1990, igic_2006}. %B: may need to introduce "S-locus" earlier.
This represents very strong evidence that the SI mechanism, and our $I$ state is ancestral to the Solanaceae, and did not arise independently within the family ($q_{CI}=0$). %B: I think I have this right <- someone please double-check.
% This is an important assumption because ancestral state reconstruction in the models might differ when polyploidy and breeding system are analyzed as independent in the Solanaceae tree.
% This irreversibility assumption prevents self-compatible state from evolving into self-incompatible state and as a result, the ancestral state of all taxa in this model has probability one of being self-incompatible.
%
%B: What happens if SC->SI is not fixed? Asking for a friend.  E: Surprisingly, Rosana reports, results are not turned on their head. 
%B: Whew, I was worried. Er, "friend" says thanks.

@@

If ploidy and breeding system each influence lineage diversification individually, it is logical to examine their possible joint effects. %B: unsure about edit, which was: "If both ploidy and breeding system have the potential to influence lineage diversification, we should logically consider their effects jointly."  E: okay; also try to add that their transitions interact
We thus fit a multi-state model that includes both traits \citep[MuSSE,][]{fitzjohn_2012}.
The three states in this model are self-incompatible diploids (ID), self-compatible diploids (CD), and polyploids, which are always self-compatible (CP).
As explained above, we did not include a state for self-incompatible polyploids because they are not observed in the data, and   that trait combination state is mechanistically predicted not to occur.
We call this the \textit{ID/CD/CP ploidy and breeding system} model.
The model has 10 parameters, six for diversification in each state ($\lambda_{ID},\ \lambda_{CD},\ \lambda_{CP}$ for speciation, $\mu_{ID},\ \mu_{CD},\ \mu_{CP}$ for extinction) and four for transitions between states ($\rho_I,\ \rho_C$ for polyploidization transitions from $ID$ and $CD$ to $CP$, respectively; $\delta$ for diploidization from $CP$ to $CD$; $q_{IC}$ for loss of self-incompatibility without polyploidization, from $ID$ to $CD$).
The total rate of loss of self-incompatibility, \ie transitions out of $ID$, is $q_{IC} + \rho_I$.
Diploidization from $CP$ to $ID$ is not allowed because it would represent a simultaneous regain of SI.

The ID/CD/CP model could potentially capture similar dynamics as earlier models, if the effects of the hidden state in D/P+A/B were effectively caused by breeding system (or its correlates), and the hidden state in I/C+A/B was effectively caused by ploidy.
There is also the potential, however, for a hidden factor to be influencing diversification beyond both of our focal traits, and this could again mislead inferences.
We therefore added a hidden trait layer on top of our three-state model \citep[analogous to][]{caetano_2018, herrera_2018, huang_2018}.
We refer to this as the \textit{ID/CD/CP+A/B} model.
A fully parameterized version of this model would have 26 rate parameters \citep{herrera_2018}. 
Because our goal was to look for diversification rate differences associated with ploidy and breeding system rather than the specific effects of the hidden states, we fitted a simplified version with 16 parameters.
The reduction in parameter space is achieved by fixing the rates for transitions among hidden states to be equal with rate $\alpha$, and fixing the transition rates between observed states to be independent of the hidden state (rates $\rho_I,\ \rho_C,\ \delta,\ q_{IC}$ as defined for the ID/CD/CP model).
There are additionally twelve diversification rate parameters ($\lambda_{ID_A},\ \lambda_{ID_B},\ \lambda_{CD_A},\ \lambda_{CD_B},\ \lambda_{CP_A},\ \lambda_{CP_B},\ \mu_{ID_A},\ \mu_{ID_B},\ \mu_{CD_A},\ \mu_{CD_B},\ \mu_{CP_A},\ \mu_{CP_B}$).
%B: I can't tell, but it seems to me that this 26->16 parameter reduction makes it possible to underestimate the effect of these hidden states. Perhaps this complication is covered in the Discussion section.

@@

For all four models that consider ploidy changes, we allowed diploidization.
Previous modeling approaches \citep{mayrose_2011} have argued against inferring diploidization rates when using ploidy data that comes from classifications based on chromosome number multiplicity or chromosome number change models like chromEvol \citep{mayrose_2010}.
These types of classifications do not allow for a ploidy reversion.
Where indicated, the classification of ploidy for the data used in our models was based on chromosome multiplicity at the genus level.
% ref data/sources table?
However, the majority of the ploidy classifications were adopted from original studies with alternative sources of information (\eg geographic distribution, genus ploidy distribution) where ploidy was defined by authors that found evidence for it.
Since it is not clear whether diploidization can be detected under alternative ploidy classifications or even classifications based on chromosome number multiplicity at the genus level, we also fit the models without diploidization in order to test  whether the conclusions about diversification are sensitive to including diploidization.
As discussed by \citet{servedio_2014}, the presence or absence of a hypothesis can have an exploratory goal.
In our case the diploidization parameter (or its absence, $\delta=0$) in our models is an opportunity to explore an assumption that might be important but that is not the single definitive process to understand the interactions among polyploidy, breeding system, and diversification.

% \subsection{Pathways to polyploidy} % E todo
% robertson2011 method, and then with diversification
% propogation matrix, stable stage structure
% avoid "probability" and "transition matrix"
% analogous to Leslie matrix?

@@

% R will add a bit about the ASR methods

@@

Using the marginal likelihood values, we calculated thirteen different Bayes factors.
Six compared the models of ploidy against one other (D/P and D/P+A/B, each with or without diploidization), one compared the breeding system models (I/C and I/C+A/B), and six compared the models with both traits (ID/CD/CP and ID/CD/CP+A/B, each with or without diploidization) (\cref{table:bayesfactors}).
%
Other comparisons between these models are not valid because the input data are different under the different state space codings (\cref{figure:stateclassifications}).
In mathematical terms, the D/P, I/C, and ID/CD/CP state spaces are not `lumpable' with respect to one another \citep{tarasov_2019}.
%R: Emma this is where the figure can be important to show that we have to make different input
% E: I think this short explanation is clear enough, especially with the figure.  I'm not sure whether the hierarchical concept is exactly applicable here.
Each model comparison is reported with a Bayes factor on the natural log scale: the comparison between models $M_0$ and $M_1$ is $BF(M_0,\ M_1) = \ln[ P(\mathbf{X} | M_0) - P(\mathbf{X} | M_1]$.
There is `positive' support for $M_0$ when this value is more than 2, `strong' support when it is more than 6, and `very strong' support when it is more than 10 \citep{kass1995}.

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{states.pdf}
\caption{
Character states used for each of the models.
Each species retained on the tree belonged to one of five possible categories, depending on whether ploidy and/or breeding system were known.
The number of species in each is shown under the corresponding circles in the top row. % FIXME: Rosana, what are the numbers for CP and ?P ?
These categories were then grouped in a manner appropriate to the states of each model.
For example, there are 34 species that are self-compatible and of unknown ploidy; these are coded as either $D$ or $P$ in the D/P models (uncertain, or consistent with either state), as $C$ in the I/C models, and as either $CD$ or $CP$ in the ID/CD/CP models.
In all cases, species were coded as either $A$ or $B$ in the hidden state models.
The models depicted in the different rows use state spaces that are not comparable with one another.
For example, we cannot test whether the D/P model fits better than the I/C model because they use states that are not the same and are not `lumpable' \citep{tarasov_2019}.
%B: Hmmm. The presentation is economical, true, and I think it is retrospectively clear, and valuable, now that I've been thinking about the paper for a while. But it will be very difficult as a source of clarity for someone reading the paper the first time. The top graphical layout also implicitly communicates the idea that all "I" species must be "D", and that all "P" species must be also "C", which is not intuited easily. (Are they encoded like that?) Moreover, it's not made clear that the 'species' in question are, in fact, often polymorphic, which makes DPIC possible. The subsequent models require a bit of thought, which is not too bad, but the treatment of the state coding and specifically the sentence "In all cases, species were coded as either A or B in the hidden state models." is a bit terse for someone not familiar with HiSSE. 
}
\label{figure:stateclassifications}
\end{figure}
